\documentclass[utf8]{article}
\usepackage{xcolor}
% ================= 设置版面，A4 页面高 29.7cm, 宽 21.0cm ================ %
% 1英寸(inch) = 2.54 cm
% 水平左边空距，默认为 1in + \hoffset %
\setlength{\hoffset}{-0.54cm}
% 垂直上边空距，默认为 1in + \voffset %
\setlength{\voffset}{-0.54cm}
% 纸张内侧边界: 水平边空距 + \oddsidemargin (奇数页的左边界) = 2.00cm %
\setlength{\oddsidemargin}{0cm}
% 纸张外侧边界: 水平边空距 + \evensidemargin (偶数页的左边界) = 2.00cm %
\setlength{\evensidemargin}{0cm}
% 版心 17.0cm + 内侧边界 2.00cm + 外侧边界 2.00cm = 21.0cm %
\setlength{\textwidth}{17.0cm}
% 上页边到页眉的距离 %
\setlength{\topmargin}{0.90cm}
% 标题行高度 %
\setlength{\headheight}{0.55cm}
% 正文到标题的间距 %
\setlength{\headsep}{0.45cm}
% 正文底部到页脚距离 %
\setlength{\footskip}{0.90cm}
% 版心高度 22.90cm + 上页边空距 2.00cm + 页边页眉距 0.90cm + 标题行高 0.55cm %
%         + 正文标题距 0.45cm + 正文页脚距 0.90cm + 下页边空距 2.00 = 29.70cm %
\setlength{\textheight}{22.90cm}
% ============================================================================== %
\renewcommand{\baselinestretch}{0}                                % 行距
\setlength{\parskip}{2.0ex plus0.1ex minus0.2ex}                 % 段落间距
%\setlength{textwidth}{400pt}
\begin{document}


\begin{flushright}
The sentence following is used for vocabulary recording.\\
\today\\
\end{flushright}

\begin{flushleft}
\begin{enumerate}
\item The authorities have \textcolor{red}{\textit{abandoned}} any attempt to distribute food in an orderly fashion.
\item The creators of the original X-man \textcolor{red}{\textit{abbreviated}} the title of its sequel of simple X2.
\item You can use your left hand to massage her breasts, \textcolor{red}{\textit{abdomen}},or clitoris.
\item I can't \textcolor{red}{\textit{abide}} dishonesty!
\item The machinist pressed his ear to the instrument in order to listen and tell where the \textcolor{red}{\textit{abnormal}} sound came from.
\item An Illinois House committee voted Thursday to \textcolor{red}{\textit{abolish}} the death penalty.
\item[-] The end of law is not \textcolor{red}{\textit{abolish}} or restrain, but to preserve and enlarge freedom.
\item Their discussion centered around the \textcolor{red}{\textit{abolition}} of slavery.
\item The steep sidewalk was too narrow for them to walk \textcolor{red}{\textit{abreast}}.
\item[-] He will be keeping \textcolor{red}{\textit{abreast}} of the news.
\item Article 33 A book publisher may alter or \textcolor{red}{\textit{abridge}} a work with the permission of the copy right owner.
\item Most analysts expect China to achieve a ``soft landing'' and avoid an \textcolor{red}{\textit{abrupt}} downturn.
\item This controls the \textcolor{red}{\textit{absorption}} of liquids.
\item His \textcolor{red}{\textit{abstracts}} are held in numerous collections.
\item But to us, the suggestion that we were in any danger was \textcolor{red}{\textit{absurd}}.
\item This area of Mexico has an \textcolor{red}{\textit{abundance}} of safe beaches and a pleasing climate.
\item[-] There is an \textcolor{red}{\textit{abundant}} supply of cheap labour.
\item He \textcolor{red}{\textit{alleged}} that he was verbally abused by other soldiers.
\item The author has settled for a more \textcolor{red}{\textit{academic}} approach.
\item At the same time, we have to keep doing everything we can to \textcolor{red}{\textit{accelerate}} this recovery.
\item This assumption played a considerable part in increasing the social \textcolor{red}{\textit{acceptability}} of divorce.
\item Yes, the pounds 300 ipod looks good and yes, it's great \textcolor{red}{\textit{accessory}} for iMac owners.
\item A policeman \textcolor{red}{\textit{accidentally}} killed his two best friends with a single bullet.
\item The school is not big enough to \textcolor{red}{\textit{accommodate}} all the children.
\item[-] The government will provide temporary \textcolor{red}{\textit{accommodation}} for up to three thousand homeless people.
\item We should make decisions in \textcolor{red}{\textit{accordance}} with specific conditions.
\item The boss dropped an \textcolor{red}{\textit{accountant}} from the payroll.
\item[-] It is the business of the scientist of accumulate knowledge about universe and all that is in it, and to find, if he is able, common factors which
underlie and \textcolor{red}{\textit{account}} for the facts that he knows.
\item Every care has been taken to ensure the \textcolor{red}{\textit{accuracy}} of all information in this leaflet.
\item[-] Police have stressed that this is the most \textcolor{red}{\textit{accurate}} description of the killer to date.
\item I was \textcolor{red}{\textit{accustomed}} to being the only child at a table full of adults.
\item[-] She has got \textcolor{red}{\textit{accustomed}} to this sort of work.
\item Battery \textcolor{red}{\textit{acid}} had eroded the engine.
\item Naylor \textcolor{red}{\textit{acknowledged}}, in a letter to the judge, that he was a drug \textcolor{red}{\textit{addict}}.
\item I will \textcolor{red}{\textit{acquaint}} you with my daughter when she arrives.
\item[-] He exchanged a few words with the proprietor, an old \textcolor{red}{\textit{acquaintance}} of his.
\item General Motors \textcolor{red}{\textit{acquired}} a 50\% stake in Saab for about \$400m.
\item How did you go about making his marvelous \textcolor{red}{\textit{acquisition}} then?
\item  I had \textcolor{red}{\textit{acupuncture}} in my lower back.
\item The war has \textcolor{purple}{\textit{aggravated}} an \textcolor{red}{\textit{acute}} economic crisis.
\item The \textcolor{red}{\textit{acrobat}} balanced himself on the high rope.
\item Most living creatures are capable of \textcolor{red}{\textit{adaptation}} when compelling to do so.
\item The \textcolor{red}{\textit{addict}} prowled about for a place to drug up.
\item[-] She helped him fight his drug \textcolor{red}{\textit{addiction}}.
\item The website provides regional weather reports, a shipping forest, and gale warning. In \textcolor{red}{\textit{addition}}, victors can download the satellite image of the US.
\item[-] The US is sending \textcolor{red}{\textit{addition}} troops to the region.
\item One in four people worldwide are without \textcolor{red}{\textit{adequate}} homes.
\item[-] She is prepared to offer me an amount \textcolor{red}{\textit{adequate}} to purchase another house.
\item All members of the association \textcolor{red}{\textit{adhere}} to a strict code of practice.
\item He sat in \textcolor{red}{\textit{adjacent}} room and waited.
%\item [@]No50 end
%\newpage
%\item[@] No187 inserted
\item She has refused to \textcolor{red}{\textit{reveal}} the whereabouts of her daughters.
\item[-] A survey of the American diet has \textcolor{red}{\textit{revealed}} that a growing number of people are overweight.
\item In the future we \textcolor{red}{\textit{envision}} a federation of companies.
\item An \textcolor{red}{\textit{antecedent}} of something happened or existed before it and was similar to it in some way.
\item[-] We shall first look briefly at the historical \textcolor{red}{\textit{antecedents}} of this theory.
\item The \textcolor{red}{\textit{antenna}} of something such as insect or crustacean are the two long, thin parts attached to its head that it used to feel things with.
\item An \textcolor{red}{\textit{anthem}} is a song that is used to represent a particular nation, society, or group and that is sung on special occasions.
\item Napping should not be \textcolor{red}{\textit{frowned}} upon at the office or make you feel guilty at home.
\item[-] When someone \textcolor{red}{\textit{frowns}}, their eyebrows become drawn together, because the are annoyed, worried, or puzzled or because they are concentrating.
\item In the old days, people would \textcolor{red}{\textit{doze}} for an hour or so after the midday meal, and in some Latin American and European countries \textcolor{red}{\textit{siestas}} are still in \textcolor{red}{\textit{vogue}}.
\item[-] When you \textcolor{red}{\textit{doze}}, you sleep lightly or for a short period, especially during the daytime.
\item[-] A \textcolor{red}{\textit{siestas}} is a short sleep or rest which you have in the early afternoon, especially in hot countries.
\item[-] If there is a \textcolor{red}{\textit{vogue}} for something, it is very popular and fashion.
\item But in most industrialized nations, the usual response to the afternoon \textcolor{red}{\textit{sag}} in energy is to try to jump-start the system with caffeine.
\item[-] When something \textcolor{red}{\textit{sags}}, it hangs down loosely or sinks downward in the middle.
\item But sleep experts say that \textcolor{red}{\textit{tactic}} is actually \textcolor{red}{\textit{counterproductive}}, creating only the illusion of efficiency and alertness and \textcolor{red}{\textit{depriving}} the body and brain of much-needed sleep.
\item[-] Something that is \textcolor{red}{\textit{counterproductive}} achieve the opposite result from the one that you want to achieve.
\item[-] \textcolor{red}{\textit{Tactics}} are the methods that you choose to use in order to achieve what you want in a particular situation.
\item[-] If you \textcolor{red}{\textit{deprive}} someone of something that they want or need, you take it away from them, or you prevent them from having it.
\item Now, however, there is growing evidence that \textcolor{red}{\textit{restorative}} naps are making a comeback.
\item[-] Something that is \textcolor{red}{\textit{restorative}} makes you feel healthier, stronger, or more cheerful after you have been tired, weak, or \textcolor{red}{\textit{miserable}}.
\item[-] If you are \textcolor{red}{\textit{miserable}}, you are very unhappy.
\item Recognizing that most of their employees are chronically sleep-deprived, some companies have set up nap rooms with \textcolor{red}{\textit{reclining}} chairs, \textcolor{red}{\textit{blankets}} and alarm clocks.
\item[-] If you \textcolor{red}{\textit{recline}} on something, you sit or lie on it with the upper part of your body supported at an angle.
\item[-] A \textcolor{red}{\textit{blanket}} is a large square or rectangular piece of thick cloth, especially one that you put on a bed to keep you warm.
\item If unions are truly interested in worker \textcolor{red}{\textit{welfare}}, they should make such accommodations a standard item in contract \textcolor{red}{\textit{negotiations}}.
\item[-] The \textcolor{red}{\textit{welfare}} of a person or group is their health, comfort, and happiness.
\item[-] \textcolor{red}{\textit{Negotiations}} are formal discussions between people who have different aims or \textcolor{red}{\textit{intentions}}, especially in business or politics, during which they try to reach an agreement.
\item[-] An \textcolor{red}{\textit{intention}} is an idea or plan of what you are going to do.
\item My college roommate, Dr. Linda Himot, a psychiatrist in Pittsburgh, who has a talent for ten-minute catnaps between patients, says these \textcolor{red}{\textit{respites}} help her focus better on each patient's problems,which are not always \textcolor{red}{\textit{scintillating}}.
\item[-] A \textcolor{red}{\textit{respite}} is a short period of rest from something unpleasant.
\item[-] A \textcolor{red}{\textit{scintillating}} conversation or performance is very lively and interesting.
\item Studies have shown that sleepy workers make more mistakes and cause more accidents, and are more \textcolor{red}{\textit{susceptible}} to heart attacks and \textcolor{red}{\textit{gastro}} intestinal disorders.
\item[-] If you are \textcolor{red}{\textit{susceptible}} to something or someone, you are very likely to be influenced by them.
\item[-] \textcolor{red}{\textit{Gastrointestinal}} means relating to the stomach and intestines.
\item Dr. David Dinges, a sleep researcher at the University of Pennsylvania, is a strong advocate of \textcolor{red}{\textit{prophylactic}} napping - taking what he and others call a "power nap" during the day to head off the cumulative effects of sleep loss.
\item[-] \textcolor{red}{\textit{Prophylactic}} means concerned with preventing disease.
\item He explained that the brain "sort of \textcolor{red}{\textit{sputters}}" when it is deprived of sufficient sleep, causing \textcolor{red}{\textit{slips}} in performance and attentiveness and often resulting in "microsleeps" - involuntary \textcolor{red}{\textit{lapses}} into sleep, in which accidents can occur.
\item[-] If something such as an engine or a flame \textcolor{red}{\textit{sputters}}, it works or burns in an uneven way and makes a series of soft popping sounds.
\item[-] If you \textcolor{red}{\textit{slip}}, you accidentally slide and lose your balance.
\item[-] A \textcolor{red}{\textit{lapse}} is a moment or instance of bad behavior by someone who usually behaves well.
\item A brief afternoon nap typically leaves people feeling more energized than if they had tried to \textcolor{red}{\textit{muddle}} through without sleeping.
\item[-] If people or things are in a \textcolor{red}{\textit{muddle}}, they are in a state of confusion or disorder.
\item He also state that "naps taken about eight hours after you wake have been proved to do much more for you than if you added those twenty minutes onto already adequate \textcolor{red}{\textit{nocturnal}} sleep."
\item[-] \textcolor{red}{\textit{Nocturnal}} means occurring at night.
\item There are two kind of naps: brief ones taken to \textcolor{red}{\textit{revive}} the brain and long ones taken to \textcolor{red}{\textit{compensate}} for
    significant sleep loss.
\item But long naps have a temporary disadvantage: they cause what researchers call sleep \textcolor{red}{\textit{inertia}}, a \textcolor{red}{\textit{groggi\\-ness}}
     upon awakening that can last about half and an hour.
\item[-] If you have a feeling of \textcolor{red}{\textit{inertia}}, you feel very lazy and unwilling to move or be active.
\item Finally, naps are often essential for people trying to work through illness, injury or \textcolor{red}{\textit{chemotherapy}}, even if they get adequate sleep
    at night.
\item \textcolor{red}{\textit{Chemotherapy}} is the treatment of disease using chemicals. It is often used in treating cancer.
\item While a slave, he had received a full \textcolor{red}{\textit{portion}} of beatings and other \textcolor{red}{\textit{indignities}}.
\item[-] A \textcolor{red}{\textit{portion}} of something is a part of it.
\item[-] If you talk about the \textcolor{red}{\textit{indignity}} of doing something, you mean that it makes you feel embarrassed or unimportant.
\item Douglass was a \textcolor{red}{\textit{majestically}} handsome man who \textcolor{red}{\textit{radiated}} determination and \textcolor{red}{\textit{indignation}}.
\item[-] The waters of the Changjiang River rolled to the east on \textcolor{red}{\textit{majestically}}.
\item[-] If things \textcolor{red}{\textit{radiate}} out from a place, they form a pattern that is like lines drawn from the centre of a circle to various points on its edge.
\item[-]  \textcolor{red}{\textit{Indignation}} is a feeling of shock and anger when you think that something is unjust or unfair.
\item Douglass insisted that \textcolor{red}{\textit{emancipation}} alone would not provide the slaves with freedom.
\item[-] We must \textcolor{red}{\textit{arouse}} them to fight for their own \textcolor{red}{\textit{emancipation}}.
\item[-] If something \textcolor{red}{\textit{arouses}} a particular reaction or attitude in people, it causes them to have that reaction or attitude.
\item But fewer still who heard him or read his works could afterward maintain that all blacks were dull-witted or \textcolor{red}{\textit{resigned}} to inferior status.
\item[-] If you \textcolor{red}{\textit{resign}} from a job or position, you formally announce that you are leaving it.
\item The Parthenon was built in Athens in the fifth century B.C. and \textcolor{red}{\textit{dedicated}} to the goddess Athena. It remains an example of near-perfect architectural design.
\item[-] If you say that someone has \textcolor{red}{\textit{dedicated}} themselves to something, you approve of the fact that they have decided to give a lot of time and effort to it because they think that it is important.
\item \textcolor{red}{\textit{Infertility}} rates have been rising over the past twenty years: 10 to 15 percent of couples who want a baby cannot conceive.
\item[-] However, no study on the prevalence of \textcolor{red}{\textit{infertility}} has been conducted in this area.
\item Beethoven came on the \textcolor{red}{\textit{scene}} at a favorable moment in history.
\item[-] A \textcolor{red}{\textit{scene}} in a play, movie, or book is part of it in which a series of events happen in the same place.
\item The educational system of the United States has long been characterized by \textcolor{red}{\textit{discriminatory}} treatment of women.
\item[-] \textcolor{red}{\textit{Discriminatory}} laws or practices are unfair because they treat one group of people worse than other groups.
\item In the twentieth century, sexism in education was \textcolor{red}{\textit{manifested}} in many ways.
\item[-]  If you say that something is \textcolor{red}{\textit{manifest}}, you mean that it is clearly true and that nobody would disagree with it if they saw it or considered it.
\item The positions of university professor and college administrator have generally been \textcolor{red}{\textit{reserved}} for man.
\item[-]  If something is \textcolor{red}{\textit{reserved}} for a particular person or purpose, it is kept specially for that person or purpose.
\item Many of us have \textcolor{red}{\textit{ambivalent}} feelings about our politicians, \textcolor{red}{\textit{admiring}} but also distrusting them.
\item[-] If you say that someone is \textcolor{red}{\textit{ambivalent}} about something, they seem to be uncertain whether they really want it, or whether they really approve of it.
\item[-] An \textcolor{red}{\textit{admiring}} expression shows that you like or respect someone or something.
\item A value is a set of bits \textcolor{red}{\textit{interpreted}} according to a type.
\item[-]  If you \textcolor{red}{\textit{interpret}} something in a particular way, you decide that this is its meaning or \textcolor{red}{\textit{significance}}.
\item[-] The \textcolor{red}{\textit{significance}} of something is the importance that it has, usually because it will have an effect on a situation or shows something about a situation.
\item A char variable is of the natural size to hold a character on a given machine (typically an 8-bit byte), and the sizes of other types are \textcolor{red}{\textit{quoted}} in multiples of the size of a char.
\item[-]  If you \textcolor{red}{\textit{quote}} someone as saying something, you repeat what they have written or said.
\item You also made \textcolor{red}{\textit{inferences}} in the chapter on \textcolor{red}{\textit{implied}} main ideas.
\item[-]  An \textcolor{red}{\textit{inference}} is a conclusion that you draw about something by using information that you already have about it.
\item[-]  If you \textcolor{red}{\textit{imply}} that something is the case, you say something that indicates that it is the case in an indirect way.
\item In \textcolor{red}{\textit{assignments}} and in arithmetic operations, C++ performs all meaningful \textcolor{red}{\textit{conversions}} between the basic types so that they can be mixed freely.
\item[-]  An \textcolor{red}{\textit{assignment}} is a task or piece of work that you are given to do, especially as part of your job or studies.
\item[-]  \textcolor{red}{\textit{Conversion}} is the act or process of changing something into a different state or form.
\item  The godswood there was a garden, bright and airy, where tall redwoods spread \textcolor{red}{\textit{dappled}} shadows across tinkling streams, birds sang from hidden nests, and the air was \textcolor{red}{\textit{spicy}} with the \textcolor{red}{\textit{scent}} of flowers.
\item  This was a wood of \textcolor{red}{\textit{stubborn sentinel}} trees armored in grey-green \textcolor{red}{\textit{needles}}, of mighty oaks, of ironwoods as old as the realm itself.
\item Here thick black trunks crowded close together while twisted branches wove a dense \textcolor{red}{\textit{canopy}} overhead and misshappen roots wrestled \textcolor{red}{\textit{beneath}} the soil.
\item \textcolor{red}{\textit{Worship}} was for the \textcolor{red}{\textit{sept}}.
\item For her \textcolor{red}{\textit{sake}}, Ned had built a small sept where she might sing to the seven faces of god, but the blood of the First Men still flowed in the \textcolor{red}{\textit{veins}} of the Starks, and his own gods were the old ones, the nameless, faceless gods of the greenwood they shared with the \textcolor{red}{\textit{vanished}} children of the forest.
\item \textcolor{red}{\textit{Dorks}} were hopelessly \textcolor{red}{\textit{inept}}.
\item[-]  If you say that someone is a \textcolor{red}{\textit{dork}}, you think they dress badly in oldfashioned clothes and behave very awkwardly in social situations.
\item[-] If you say that someone is \textcolor{red}{\textit{inept}}, you are criticizing them because they do something with a complete lack of skill.
\item Kids typically date only within their status level, which is set in stone by the first year and \textcolor{red}{\textit{seldom}} can be upgraded.
\item[-] If something \textcolor{red}{\textit{seldom}} happens, it happens only occasionally.
\item High school is a very \textcolor{red}{\textit{scary}} place.
\item[-]  Something that is \textcolor{red}{\textit{scary}} is rather frightening.
\item To take the pressure off at home, consider cutting teens some \textcolor{red}{\textit{slack}} on minor \textcolor{red}{\textit{disputes}}, he advises.
\item[-] Something that is \textcolor{red}{\textit{slack}} is loose and not firmly stretched or tightly in position.
\item[-] A \textcolor{red}{\textit{dispute}} is an argument or disagreement between people or groups.
\item No matter how it looks, they're \textcolor{red}{\textit{desperate}} for love.
\item[-] If you are \textcolor{red}{\textit{desperate}}, you are in such a bad situation that you are willing to try anything to change it.
\item Within moments of a \textcolor{red}{\textit{torpedo's}} impact, reports a survior, stunned men were pouring out from their \textcolor{red}{\textit{bunks}} as the ship began \textcolor{red}{\textit{tilting}}.
\item[-] A \textcolor{red}{\textit{torpedo}} is a bomb that is shaped like a tube and that travels under water.
\item[-] A \textcolor{red}{\textit{bunk}} is a narrow bed that is usually attached to a wall, especially in a ship.
\item[-] If you \textcolor{red}{\textit{tilt}} an object or if it tilts, it moves into a sloping position with one end or side higher than the other.
\item With power cut off, the \textcolor{red}{\textit{escort vessels}}, unaware of the unfolding \textcolor{red}{\textit{tragedy}}, pushed on in the darkness.
\item[-] If you \textcolor{red}{\textit{escort}} someone somewhere, you accompany them there, usually in order to make sure that they leave a place or get to their destination.
\item[-] A \textcolor{red}{\textit{vessel}} is a ship or large boat.
\item[-] A \textcolor{red}{\textit{tragedy}} is an extremely sad event or situation.
\item Onboard, chaos ruled as \textcolor{red}{\textit{panicky}} men came up from the hold without life jackets and leaped into overcrowded lifeboats.
\item[-] A \textcolor{red}{\textit{panicky}} feeling or panicky behaviour is characterized by panic.
\item When the four \textcolor{red}{\textit{chaplains}} made it up to the \textcolor{red}{\textit{steeply sloping}} deck, they began guiding the men to their boat stations.
\item[-] A \textcolor{red}{\textit{chaplain}} is a member of the Christian clergy who does religious work in a place such as a hospital, school, prison, or in the armed forces.
\item[-] A \textcolor{red}{\textit{slope}} is the side of a mountain, hill, or valley.
\item George Washington's honesty is a \textcolor{red}{\textit{trait}} that has been well publicized.
\item[-] A \textcolor{red}{\textit{trait}} is a particular characteristic, quality, or tendency that someone or something has.
\item \textcolor{red}{\textit{Substantial(Feedback Control Theory P.2)}} means large in amount or degree.
\item Tell them \textcolor{red}{\textit{explicitly (Feedback Control Theory P.2)}} you want to continue the friendship.
\item A \textcolor{red}{\textit{specification(Feedback Control Theory P.2)}} is a requirement which is clearly stated, for example about the necessary features in the design of something.
\item If you say that someone \textcolor{red}{\textit{manipulates(Feedback Control Theory P.3)}} people, you disapprove of them because they skilfully force or persuade people to do what they want.
\item \textcolor{red}{\textit{Equilibrium(Feedback Control Theory P.3)}} is a balance between several different influences or aspects of a situation.
\item \textcolor{red}{\textit{Norms(Feedback Control Theory P.3)}} are ways of behaving that are considered normal in a particular society.
\item There will be some improvement in experience at the outset, just not as much as the processor \textcolor{red}{\textit{specs (Feedback Control Theory P.3)}} promise.
\item A \textcolor{red}{\textit{lump(Feedback Control Theory P.4)}} of something is a solid piece of it.
\item \textcolor{red}{\textit{Rational(Feedback Control Theory P.6)}} decisions and thoughts are based on reason rather than on emotion.
\item If you refer to a government or system of running a country as a \textcolor{red}{\textit{regime(Feedback Control Theory P.4)}}, you are critical of it because you think it is not democratic and uses unacceptable methods.
\item You use \textcolor{red}{\textit{nominal(Feedback Control Theory P.4)}} to indicate that someone or something is supposed to have a particular identity or status, but in reality does not have it.
\item A \textcolor{red}{\textit{perturbation(Feedback Control Theory P.4)}} is a small change in the movement, quality, or behaviour of something, especially an unusual change.
\item So a \textcolor{red}{\textit{priori(Feedback Control Theory P.4)}}, this was not necessarily true.
\item A \textcolor{red}{\textit{coefficient(Feedback Control Theory P.4)}} is a number that expresses a measurement of a particular quality of a substance or object under specified conditions.
\item If something \textcolor{red}{\textit{fluctuates(Feedback Control Theory P.5)}}, it changes a lot in an irregular way.
\item With \textcolor{red}{\textit{exogenous(Feedback Control Theory P.6)}} red-lights flashing brightly in the euro zone, demand for the dollar is building.
\item Turn off your \textcolor{red}{\textit{thermostat(Feedback Control Theory P.6)}} when you’re not home.
\item But this agreement has quickly turned into an argument about which institution should be the \textcolor{red}{\textit{super-regulator(Feedback Control Theory P.6)}}, and whether such responsibilities can be split.
\item They \textcolor{red}{\textit{throttled(Feedback Control Theory P.6)}} the watchman and robbed the bank.
\item Portable \textcolor{red}{\textit{pedal(Feedback Control Theory P.6)}} machines could be used in every office to improve the health of workers, according to scientists in the US.
\item A \textcolor{red}{\textit{gust(Feedback Control Theory P.6)}} of wind made the torches flare.
\item In this case, the set of proposals is not \textcolor{red}{\textit{restricted(Feedback Control Theory P.7)}}.
\item Now try to find a \textcolor{red}{\textit{rational(Feedback Control Theory P.7)}} reason for each one.
\item This map shows the \textcolor{red}{\textit{layout(Feedback Control Theory P.7)}} of the plant.
\item The models, though, disagree widely in the \textcolor{red}{\textit{magnitude(Feedback Control Theory P.7)}} of the warming we can expect.
\item Ideally, I would expect the word dictionary to grow \textcolor{red}{\textit{asymptotically(Feedback Control Theory P.8)}} as more files are indexed.
\item If you separate the operations that can throw an exception from those that can't, the problem becomes more \textcolor{red}{\textit{tractable(Feedback Control Theory P.8)}}.
\end{enumerate}
\end{flushleft}
\end{document}
